---
title: "SI Week 2 Homework"
output:
    html_document:
        keep_md: true
---

## Question 1

The probability that a manuscript gets accepted to a journal is 12% (say). However, given that a revision is asked for, the probability that it gets accepted is 90%. Is it possible that the probability that a manuscript has a revision asked for is 20%?

- Yeah, that's totally possible
- No, it's not possible
- It's not possible to answer this question

$$
A = \mbox{Accepted} \\
B = \mbox{Revision requested} \\
P(A) = .12 \\
P(B) = .20 \\
P(A ~|~ B) = .90 \\
P(A \cap B) = P(A ~|~ B) * P(B) = 0.90 * 0.20 = 0.18
$$

So, no, because it suggests that $P(A \cap B) > P(A)$.

[https://www.youtube.com/watch?v=E4kE4M1J15s&feature=youtu.be&list=PLpl-gQkQivXhHOcVeU3bSJg78zaDYbP9L](Answer)

## Question 2

Suppose that the number of web hits to a particular site are approximately normally distributed with a mean of 100 hits per day and a standard deviation of 10 hits per day. What's the probability that a given day has fewer than 93 hits per day expressed as a percentage to the nearest percentage point?

- 76%
- 24%
- 47%
- 94%

```{r}
round(pnorm(93, mean=100, sd=10) * 100, 0)
```

## Question 3

Suppose 5% of housing projects have issues with asbestos. The sensitivity of a test for asbestos is 93% and the specificity is 88%. What is the probability that a housing project has no asbestos given a negative test expressed as a percentage to the nearest percentage point?

- 0%
- 5%
- 10%
- 20%
- 50%
- 100%

$$
A = \mbox{Prevalence of Asbestos} \\
+ = \mbox{Positive Test} \\
- = \mbox{Negative Test} \\
P(+ ~|~ A) = .93 \\
P(- ~|~ A^C) = .88 \\
P(A) = .05 \\ \\ \\
\begin{eqnarray*}
P(A^C ~|~ -)
& = & \frac{P(A^C \cap -)}{P(A^C)} \\
& = & \frac{P(- ~|~ A^C)P(A^C)}{P(- \cap A^C) + P(- \cap A)} \\
& = & \frac{P(- ~|~ A^C)P(A^C)}{P(- ~|~ A^C)P(A^C) + P(- ~|~ A)P(A)} \\
& = & \frac{P(- ~|~ A^C)(1 - P(A))}{P(- ~|~ A^C)(1 - P(A)) + (1 - P(+ ~|~ A))P(A)} \\
& = & \frac{.88 * (1 - .05)}{.88 * (1 - .05) + (1 - .93) * .05} \\
& = & \frac{.88 * .95}{.88 * .95 + .07 * .05} \\
& = & \frac{.836}{.836 + 0.0035} \\
& = & \frac{.836}{0.8395} \\
& = & .996 \approx 100\%
\end{eqnarray*}
$$

## Question 4

Suppose that the number of web hits to a particular site are approximately normally distributed with a mean of 100 hits per day and a standard deviation of 10 hits per day.

1. What number of web hits per day represents the number so that only 5% of days ahve more hits? Express your answer to 3 decimal places.

```{r}
round(qnorm(.95, mean=100, sd=10), 3)
```

## Question 5

Suppose that the number of web hits to a particular site are approximately normally distributed with a mean of 100 hits per day and a standard deviation of 10 hits per day

1. Imagine taking a random sample of 50 days. What number of web hits would be the point so that only 5% of averages of 50 days of web traffic have more hits? Express your answer to 3 decimal places.

```{r}
round(qnorm(.95, mean = 100, sd = 100 / sqrt(50)), 3)
```

## Question 6

You don't believe that your friend can discern good wine from cheap. Assuming that you're right, in a blind test where you randomize 6 paired varieties (Merlot, Chianti, ...) of cheap and expensive wines.

1. What is the chance that she gets 5 or 6 right expressed as a percentage to one decimal place?

```{r}
round(pbinom(4, size=6, prob=.5, lower.tail=F)*100, 1)
```

## Question 7

Consider a uniform distribution. If we were to sample 100 draws from a uniform distribution (which has mean 0.5 and variance 1/12) and take their mean, $\bar X$

1. What is the approximate probability of getting as large as 0.51 or larger expressed to 3 decimal places?

```{r}
mu <- .5
sigma <- 1/12
n <- 100
se <- sqrt(1/12) / sqrt(n)
round(pnorm(.51, mean=mu, sd=se, lower.tail=F), 3)
```

## Question 8 - 9

If you roll ten standard die, take their average, then repeat this process over and over and construct a histogram

1. What would it be centered at?

3.5

2. What would be it's variance expressed to 3 decimal places?

```{r}
n <- 10
sigma <- 2.92
round(sigma / n, 3)
```

## Question 10

The number of web hits to a site is Poisson with mean 16.5 per day

1. What is the probability of getting 20 or fewer in 2 days expressed as a percentage to one decimal place?

```{r}
round(ppois(20, lambda = 16.5 * 2) * 100, 1)
```