---
title: "SI Week 3 Homework"
output:
    html_document:
        keep_md: true
---

## Question 1

Load the dataset `mtcars` in the `datasets` R package. Calculate a 95% confidence interval to the nearest MPG for the variable `mpg`.

What is the confidence interval?

```{r, warning=FALSE, message=FALSE}
library(datasets)
data(mtcars)
t.test(mtcars$mpg)
```

**ANSWER:** 17.91768    22.26357

## Question 2

Suppose that standard deviation of 9 paired differences is 1. What value would the average difference have to be so that the lower endpoint of a 95% students t confidence interval touches zero?

$$
n = 9 \\
df = n - 1 = 8 \\
s = 1 \\
t = ?
$$

```{r}
n <- 9
s <- 1
df <- n - 1
qt(.975, df)
```

$$
t = 2.306004 \\ \\
\begin{eqnarray*}
0 & = & \bar X - t_{.975,df} \times \frac{s}{\sqrt n} \\ \\
\bar X
& = & t_{.975,df} \times \frac{s}{\sqrt n} \\ \\
& = & 2.306004 \times \frac{1}{\sqrt 9}
\end{eqnarray*}
$$

```{r}
n <- 9
df = n - 1
s = 1
se = s / sqrt(n)
round(qt(.975, df=df) * se, 2)
```

**ANSWER:** 0.77

## Question 3

An independent group Student's T interval is used instead of a paired T inverval when:

- The observations are paired between groups
- The observations between the groups are naturally assumed to be statistically independent **<-- ANSWER**
- As long as you do it correctly, either is fine
- More details are needed to answer the question

## Question 4

Consider the `mtcars` dataset. Construct a 95% T interval for MPG compairing 4 to 6 cylinder cars (subtracting in the order of 4 - 6) assume a constant variance. Round to 1 decimal place

```{r}
mpg4 <- mtcars[which(mtcars$cyl == 4),"mpg"]
mpg6 <- mtcars[which(mtcars$cyl == 6),"mpg"]
round(t.test(mpg4, mpg6, var.equal=T)$conf, 1)
```

## Question 5

If someone put a gun to your head and said "Your confidence interval must contain what it's estimating or I'll pull the trigger", what would be the smart thing to do?

- Make your interval as wide as possible **<-- ANSWER**
- Make your interval as small as possible
0 Call the authorities

## Question 6

Refer back to compairing MPG for 4 versus 6 cylinders. What do you conclude?

- The interval is above zero, suggesting 6 is better than 4 in terms of MPG
- The interval is above zero, suggesting 4 is better than 6 in terms of MPG **<-- ANSWER**
- The interval does not tell you anything about the hypothesis test; you have to do the test
- The interval contains 0 suggesting no difference

## Question 7

Suppose that 18 obese subjects were randomized, 9 each, to a new diet pill and a placebo. Subjects' body mass indices (BMIs) were measured at a baseline and again after having received the treatment or placebo for four weeks. The average difference from followup to the baseline (followup - baseline) was 3 kg/m$^2$ for the treated group and 1 kg/m$^2$ for the placebo group. The corresponding standard deviations of the differences was 1.5 kg/m$^2$ for the treatment group and 1.8 kg/m$^2$ for the placebo group. The study aims to answer whether the change in BMI over the four week period appear to differ between the treated and placebo groups

What is the pooled variance estimate to two decimal places?

```{r}
test.mn <- 3
test.sd <- 1.5
test.n <- 9
test.df <- test.n - 1
control.mn <- 1
control.sd <- 1.8
control.n <- 9
control.df <- control.n - 1
sp <- (test.df * test.sd^2 + control.df * control.sd^2)/(test.df + control.df)
round(sp, 2)
```

**ANSWER:** 2.75

## Question 8

For binomial data the maximum likelihood estimate for the probability of a success is

- The proportion of successes **<-- ANSWER**
- The proportion of failures
- A shrunken version of the proportion of successes
- A shrunken version of the proportion of failures

## Question 9

Bayesian inference requires

- A type I error rate
- Setting your confidence level
- Assigning a prior probability distribution **<-- ANSWER**
- Evaluating frequency error rates