---
title: "T Confidence Intervals - Exercises"
output:
    html_document:
        keep_md: true
---

## Question 1

For iid Gaussian data, the statistic $\frac{\bar X - \mu}{s / \sqrt n}$ must follow a:

- Z distribution
- t distribution **<-- ANSWER**

## Question 2

Paired differences T confidence intervals are useful when:

- Pairs of observations are linked, such as when there is subject level matching or in a study with baseline and follow-up measurements on all participants **<-- ANSWER**
- When there was randomization of a treatment between two independent groups

## Question 3

The assumption that the variances are equal for the independent group T interval means that:

- The sample variances have to be nearly identical
- The population variances are identical, but the sample variances may be different **<-- ANSWER**

## Question 4

Load the data set `mtcars` in the `datasets` R package. Calculate a 95% confidence interval to the nearest MPG for the variable `mpg`

```{r}
library(datasets)
data(mtcars)
t.test(mtcars$mpg)$conf
```

## Question 5

Suppose that standard deviation of 9 paired differences is 1. What value would the average difference have to be so that the lower end point of a 95% student's t confidence interval touches 0

$$
n = 9 \\
sd = 1 \\ \\
\begin{eqnarray*}
\bar Y_d - t_{.975} \times \frac{sd}{\sqrt n} & = & 0 \\
\bar Y_d - t_{.975} \times \frac{1}{3} & = & 0 \\
\bar Y_d & = & t_{.975} \times \frac{1}{3} \\
\bar Y_d & = & \frac{t_{.975}}{3}
\end{eqnarray*}
$$

```{r}
qt(.975, 8) / 3
```

## Question 6

An independent group Student's T interval is used instead of a paired T interval when:

- The observations are paired between the groups
- The observations between the groups are naturally assumed to be statistically independent **<-- ANSWER**
- As long as you do it correctly, either is fine
- More details are needed to answer this question

## Question 7

Consider the `mtcars` dataset. Construct a 95% T interval for MPG comparing 4 to 6 cylinder cars (subtracting in the order of 4 - 6). Assume a constant variance

```{r}
library(datasets)
data(mtcars)
sub_mtcars <- subset(mtcars, cyl %in% c(4, 6))
t.test(mpg ~ cyl, paired=F, var.equal=T, data=sub_mtcars)$conf
```

## Question 8

## Question 9

## Question 10

## Question 11